Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal distribution

### 2018-05-25 manuscript.tex
updated section 1

When working with radial velocities (RV's), the main limitation to the detection of small-mass exoplanets is not anymore the precision of the instruments used, but the different noises induced by the stars we are observing \citep[][]{Dumusque:2017aa}. Indeed, stellar oscillations, granulation phenomena and stellar activity all induce RV signals \citep{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} that are beyond the meter-per-second precision reached by the best high-resolution spectrographs. It is therefore mandatory to understand better stellar signals and to find ways to correct for them, if in the near future we want to detect or confirm an Earth-twin planet using the RV technique. This is even more true now that instrument like ESPRESSO \citep{Pepe-2014} and EXPRESS \citep{fischer2016state} should have the stability to detect such signals. However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging.

@@

Among the different stellar signals we are aware of, the one that is the most difficult to characterize and to correct for is the signal induced by stellar activity. Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, inducing spurious RV's variations \citep{Meunier-2010a, Dumusque-2014b}. In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, that will shift the entire stellar spectrum and stellar activity, that modifies the shape of spectral lines and by doing so create a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}. However, on quiet GKM dwarfs, the main target for precise RV's measurements, stellar activity induce signals of a few \ms. This corresponds physically to variations smaller than 1/100th of a pixel on the detector.

To be able to measure such tiny variations, we average the information of all the lines in the spectrum by cross correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}. The result of this operation gives us the cross-correlation function (CCF). To measure the Doppler-shift between different spectra and therefore to retrieve the RV's of a star as a function of time, we calculate the variations of the CCF barycenter. The barycenter is generally estimated by fitting a Normal distribution to the CCF and taking its mean. Variations in line shape between different spectra, which indicate the presence of signals induced by stellar activity, is measured by analysing the different moments of the CCF. Usually, the width of the CCF is estimated using the FWHM of the fitted Normal distribution, and its asymmetry using the the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.

>>>>

When working with radial velocities (RV's), one of the main limitations to the detection of small-mass exoplanets is no longer the precision of the instruments used, but the different sources of variability induced by the stars \citep[][]{Dumusque:2017aa} \jessi{We should add more citations here to new spectrographs...maybe EXPRES?}. 
Stellar oscillations, granulation phenomena, and stellar activity can all induce apparent RV signals \citep{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} that are beyond \jessi{what is meant by the word ``beyond'' here? Do you mean below the limit or above?  I think you mean above since they can induce singles that are greater than 1m/s, but we need to unambiguous here since this is a crucial point.  Beyond could also mean it is below the limit so hasn't been a concern.} the meter-per-second precision reached by the best high-resolution spectrographs \citep{fischer2016state}. \jessi{It seems the 1m/s spectrographs should be cited here...HARPS?}
%
It is therefore mandatory to better understand stellar signals and to develop methods to correct for them, if in the near future we want to detect or confirm an Earth-twin planet using the RV technique. This is even more true now that instrument like the Echelle SPectrograph for Rocky Exoplanet and Stable Spectroscopic Observations (ESPRESSO) \citep{Pepe-2014} and EXtreme PREcision Spectrometer (EXPRES) \citep{fischer2016state} should have the stability to detect such signals. However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging and false detections could plague the field.

@@

One of the most challenging stellar signal to characterize and to correct for is the signal induced by stellar activity. 
Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, which can induce spurious RV's variations \citep{Meunier-2010a, Dumusque-2014b}. 
In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and stellar activity, which modifies the shape of spectral lines and by doing so create a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}. 
However, on quiet GKM dwarfs, the main target for precise RV's measurements, stellar activity can induce signals of a few \ms. This corresponds physically to variations smaller than 1/100th of a pixel on the detector. \jessi{it seems the previous sentence is missing further justification for how it relates to the sentence that proceeds it.  Do we want to add something like, ``...smaller than 1/100th of a pixel on the detector making the changing shape of the spectral lines challenging to detect.''?}

In order to measure such tiny variations, a common approach is to average the information of all the lines in the spectrum by cross correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}. The result of this operation gives us the cross-correlation function (CCF).  The CCF gives the spectrum's cross-correlation with the template as the template is shifted according to different RVs.
%
To measure the Doppler-shift between different spectra and therefore to retrieve the RV's of a star as a function of time, the variations of the CCF barycenter are calculated. 
The barycenter is generally estimated by fitting a Normal density to the CCF and retaining its mean. Variations in line shape between different spectra, which indicate the presence of signals induced by stellar activity, are measured by analyzing the different moments of the CCF. Usually, the width of the CCF is estimated using the full-width half-maximum (FWHM) of the fitted Normal density, and its asymmetry using the the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
